My title

### 2024-11-24 paper/paper.qmd
removed posterior checks since i made a linear regression model

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

@@

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

@@

1.  **Residuals vs. Fitted**: The residuals display a somewhat random scatter around the zero line, indicating that the linearity assumption is largely met. However, slight deviations suggest potential minor nonlinearity, particularly in specific ranges of fitted values. This indicates room for improvement but does not severely undermine the model's reliability.

>>>>

@@

@@

1.  **Residuals vs. Fitted**: The residuals display a somewhat random scatter around the zero line, indicating that the linearity assumption is largely met. However, slight deviations suggest potential minor non linearity, particularly in specific ranges of fitted values. This indicates room for improvement but does not severely undermine the model's reliability.
